% © 2022 TNG Technology Consulting
%
% SPDX-License-Identifier: CC-BY-4.0
% 
% Access & Secrets
\AccessSecrets{2}{Missing access review}{We grant permissions to 3rd parties (e.g. CI/CD systems), but do not review them regularly.}
\AccessSecrets{3}{Long-living secrets}{Our secrets are long-lived and can be reused when they get leaked.}
\AccessSecrets{4}{No password policy}{We don't enforce strong passwords for cloud access, so brute-forcing is possible.}
\AccessSecrets{5}{Access to credentials}{We (as developers) have access to technical credentials.}
\AccessSecrets{6}{Slow credential rotation}{We don't propagate changes in permissions quickly enough throughout the whole system.}
\AccessSecrets{7}{Repudiation}{We can't trace back whether authenticated users/developers granted themselves additional permissions.}
\AccessSecrets{8}{No least privilege}{We don't restrict permissions (developers, technical users) to the minimum, allowing for a privilege escalation.}
\AccessSecrets{9}{Privilege escalation}{Our Identity and Access Management lets authenticated users/developers grant themselves additional permissions.}
\AccessSecrets{10}{No MFA}{We don't enforce MFA for developer access.}
\AccessSecrets{J}{Secrets in artifacts}{Our deployment artifacts contain secrets that can be extracted.}
\AccessSecrets{Q}{Complex IAM}{Our Identity and Access Management is too complex.}
\AccessSecrets{K}{Poor secrets management}{We don't use an established solution for credential management.}
\AccessSecrets{A}{Secrets in source code}{Our source code contains secrets.}
%
% Delivery
\Delivery{2}{No SBOM}{We don't know the versions of our dependencies or whether they are up to date.}
\Delivery{3}{Bundled devDependencies}{We include unneeded dependencies when deploying our system (test, build, compile-time dependencies).}
\Delivery{4}{Dependency confusion}{We don't know the source repository of our dependencies.}
\Delivery{5}{Rogue dependencies}{We don't know how a new version of a dependency changes our system.}
\Delivery{6}{Unattended updates}{Our system can be re-deployed by a change in an external dependency.}
\Delivery{7}{Missing vulnerability scans}{We don't know whether our dependencies introduce security issues.}
\Delivery{8}{Outdated dependencies}{We use outdated dependencies of our runtime platform (OS, container image, serverless runtime).}
\Delivery{9}{Dubious dependencies}{We use untrustworthy dependencies (unmaintained, used by too few people, developed by single developers, ...).}
\Delivery{10}{Missing network control}{We don't limit ingress or egress when running CI pipelines.}
\Delivery{J}{Insufficient SCM}{We don't know when someone injects code into our codebase.}
\Delivery{Q}{No source code integrity}{We are not certain which code/artifacts we are deploying.}
\Delivery{K}{Silent pipeline runs}{We won't notice when a deployment is started from a developer account.}
\Delivery{A}{Silent pipeline changes}{We won't notice when someone alters the deploy pipeline.}
%
% Recovery
\Recovery{2}{-}{-}
\Recovery{3}{No restore}{We have backups but do not check regularly whether we can restore them or not.}
\Recovery{4}{No infrastructure backups}{We have no backups for our infrastructure (IaC and its state).}
\Recovery{5}{No backups of data}{We have no backups of our application data.}
\Recovery{6}{No backups of secrets}{We have no backups for our secrets.}
\Recovery{7}{No infrastructure rollback}{We cannot restore our infrastructure to a previous state.}
\Recovery{8}{No application rollback}{We cannot restore our application to a previous state.}
\Recovery{9}{No system rollback}{We cannot restore our complete environment to a previous state.}
\Recovery{10}{Unsafe data deletions}{We don't create backups before deleting important data.}
\Recovery{J}{No backup redundancy}{All our backups can be destroyed at once, due to lack of redundancy.}
\Recovery{Q}{Missing backup integrity}{We can't tell whether our backup has been modified.}
\Recovery{K}{Broad delete permissions}{We can have the same person deleting resources and their backups.}
\Recovery{A}{No disaster recovery plan}{We have no disaster recovery plan.}
%
% Monitoring
\Monitoring{2}{-}{-}
\Monitoring{3}{-}{-}
\Monitoring{4}{-}{-}
\Monitoring{5}{Information disclosure}{We don't restrict access to the sensitive parts of our logs.}
\Monitoring{6}{Insufficient traceability}{We can't easily identify useful information in logs.}
\Monitoring{7}{Missing cost alerting}{We won't get an alert if an end user generates huge cloud bills for us.}
\Monitoring{8}{No log integrity}{We don't notice if an authenticated attacker/developer deactivates or manipulates our tools for traceability.}
\Monitoring{9}{No audits for prod access}{We don't know if an authenticated attacker/developer accessed the production environment.}
\Monitoring{10}{Insufficient monitoring}{We cannot react to problems in time because our monitoring has blind spots.}
\Monitoring{J}{Unclear alerts}{We need too long to figure out what an alert means.}
\Monitoring{Q}{No incident response plan}{We do not know how to react when our monitoring sends alerts.}
\Monitoring{K}{Inaccessible logs}{We can't access our logs if the production environment goes down.}
\Monitoring{A}{Secrets in logs}{We write secrets/personal data to our logs.}
%
% Resources
\Resources{2}{-}{-}
\Resources{3}{-}{-}
\Resources{4}{Unreachable contact details}{We can't get contacted by our cloud provider in case of emergency.}
\Resources{5}{Non-compliance}{We don't regularly check compliance with our internal policy for using/configuring cloud resources.}
\Resources{6}{Missing rate limits}{We have not configured any rate limits for our services.}
\Resources{7}{Missing resource limits}{We have no configured resource limits.}
\Resources{8}{Excessive capabilities}{We can deploy applications with excessive capabilities.}
\Resources{9}{Single point of failure}{Our whole system can be affected by a single rogue service.}
\Resources{10}{Missing ingress control}{We don't control ingress traffic.}
\Resources{J}{Missing egress control}{We don't control egress traffic.}
\Resources{Q}{Missing env separation}{Our production and staging environments are connected, either directly or indirectly (e.g. via CI/CD).}
\Resources{K}{Public resources}{Our cloud resources are publicly exposed without any need.}
\Resources{A}{No cloud policy}{We have no clear policy for using/configuring cloud resources.}
